### 2023-04-06 manuscript.tex
update data availability [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/12227c9d6a0137ad76ddd09b3edff0658db324f6.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/12227c9d6a0137ad76ddd09b3edff0658db324f6/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/4631990689

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/c4160bdfd13a7551c2f1a93a42945fb0618132d6/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/c4160bdfd13a7551c2f1a93a42945fb0618132d6}{MMV-Lab/im2im-paper@c4160bd}
on April 6, 2023.

@@

In general, all data used in this work were from open-accessible public repositories, released with other publications under open-source licenses. The scripts we used to download and re-organize the data can be found in our release repository: https://github.com/MMV-Lab/mmv\_im2im/tree/main/paper\_configs/prepare\_data. Detailed information about each dataset is listed below, in the same order as the Results section.

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/12227c9d6a0137ad76ddd09b3edff0658db324f6/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/12227c9d6a0137ad76ddd09b3edff0658db324f6}{MMV-Lab/im2im-paper@12227c9}
on April 6, 2023.

@@

In general, all data used in this work were from open-accessible public repositories, released with other publications under open-source licenses. All data used in this work were only for research purpose, and we confirm that we didn't use these for any other non-commercial purpose or commercial purpose. The scripts we used to download and re-organize the data can be found in our release repository: https://github.com/MMV-Lab/mmv\_im2im/tree/main/paper\_configs/prepare\_data. Detailed information about each dataset is listed below, in the same order as the Results section.
